Toward Centrally Programming Distributed Control Planes

### 2016-01-23 paper/expressiveness.tex
quasi-proof of stability.

The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}. If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes. Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}. Assume that there is a dispute wheel. Then that means each node $u_i$ in the dispute wheel prefers to go through

>>>>

\begin{figure}[t!]
\includegraphics[width=\columnwidth]{figures/dispute-wheel}
\label{fig:dispute-wheel}
\caption{Product graph for a dispute wheel.}
\end{figure}

The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}. If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes. Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}. Assume that the preferences in the policy describe a dispute wheel, and we will show that our failure check will reject the policy. Informally, a dispute wheel occurs when there are some number of nodes $u_1, \dots, u_n$ attempting to get a path to a destination node $d$. Each node $u_i$ prefers to go through its neighbor $u_{i+1}$ over route $R_i$ than directly to $d$ with route $Q_i$. Thus the nodes form a wheel of preferences. The product graph for a policy that contains a dispute wheel will look like Figure~\ref{fig:dispute-wheel}, which shows a dispute wheel of size 3. In order to pass the failure safety check for the compiler, the more-preferred node for $u_2$ will need to have a superset of the paths starting from the less-preferred node for $u_2$. In turn, this means that the maximum length path after visiting the more preferred $u_2$ will be $max(Z) = 1 + max(Y)$, similarly, if we look at $u_1$, we will determine that $max(Y) = 1 + max(X)$, and so on. The resulting equations define a system of unsatisfiable equations. Therefore, it is not possible for \sysname to compile a BGP policy that contains a dispute wheel. Since no-dispute-wheel is a sufficient condition for BGP stability, any compiled \sysname policy will be stable.
